---
title: "an588-week2"
author: "Ben Peters"
date: "2025-01-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

this is written in R markdown, in R studio

#WE HAVE HEADERS

tbh I'm not entirely sure what else we're supposed to be taking notes on, most of the class was just taken up by adding version control and linking git with Rstudio, which seems like the kind of thing I'd just fall back on the given tutorials for assuming I couldn't just intuit it myself.

#Some useful commands:

##Set the github account for your computer to use/push to:'
in computer terminal/shell:
```{r eval=FALSE}
git config --global user.email your email address
git config --global user.name your GitHub username
```

##Add a personal access token (classic) for Rstudio to use:

in the Rstudio console:
```{r eval=FALSE}
install.packages("gitcreds")
library(gitcreds)
gitcreds_set()
```

##Getting a new Personal Access Token from Github
the personal access token can be generated by going to (on the github website) settings>developer settings>Personal Access Tokens>Generate New Token 
and then just make sure you're generating a classic token instead of whatever the new thing is
once it's generated just copy and paste it and then input it into the prompt that pops up when you use the trio of commands above, remember you won't be able to see the token again after the first time you generate it!


#Quotes and the like
let's add a break and maybe a quote or two:

***
>These are the countries which are subject unto me, and by the grace of Ahuramazda I became king of them: Persia [Pârsa], Elam [Ûvja], Babylonia [Bâbiruš], Assyria [Athurâ], Arabia [Arabâya], Egypt [Mudrâya], the countries by the Sea [Tyaiy Drayahyâ (Phoenicia)], Lydia [Sparda], the Greeks [Yauna (Ionia)], Media [Mâda], Armenia [Armina], Cappadocia [Katpatuka], Parthia [Parthava], Drangiana [Zraka], Aria [Haraiva], Chorasmia [Uvârazmîy], Bactria [Bâxtriš], Sogdia [Suguda], Gandhara [Gadâra], Scythia [Saka], Sattagydia [Thataguš], Arachosia [Harauvatiš] and Maka [Maka]; twenty-three lands in all.

- Darius the Great
***

#Complaining about Python
Did you know python doesn't actually allow you to do proper multiprocessing? It just emulates it in the shoddiest way imaginable. I spent three months trying to figure out how to do it using the multiprocessing::pool function, after I'd been using python for less than a month total. It was not fun. The snake and I are on better terms now but it's still really jank and I'm not a fan.

#A Guess
I guess this is prettier
